\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\InputIfFileExists{secrets.tex}{}{
    \newcommand{\phone}{(555) 555-5555}
    \newcommand{\displayphone}{5555555555}
    \newcommand{\email}{email@example.com}
  }

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumePublicationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{p{0.82\textwidth}@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \multicolumn{2}{p{0.97\textwidth}}{\textit{\small#3}} \\
      \multicolumn{2}{p{0.97\textwidth}}{{\small#4}}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Fawwaz Abrial Saffa} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:\phone}\displayphone\
    $|$
    \faAt \hspace{.5pt} \href{mailto:\email}\email\
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/fawwazsaffa}{@fawwazsaffa}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/fawwazabrials}{@fawwazabrials}
    % $|$
    % \faGlobe \hspace{.5pt} \href{https://fawwazabrials.github.io}{Portfolio}
\end{center}


%----------- WORK EXPERIENCE -----------
\section{Experience}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {PT Fungsitama Cipta Teknologi}{Jakarta, Indonesia (Remote)}
            {Full-stack Developer}{Sep 2025 \textbf{--} Dec 2025, Contract}
            \resumeItemListStart            
                \resumeItem{Built ERP web and mobile APIs using Next.js, delivering HR modules (scheduling, absence, org charts) for a national-scale system.}
                \resumeItem{Optimized SQL queries and joins, reducing system load time by 20\%.}
            \resumeItemListEnd
        
        \resumeSubheading
            {Laboratorium Metaverse STEI ITB}{Bandung, Indonesia}
            {Lab Assistant}{Sep 2025 \textbf{--} Present, Part-time}
            \resumeItemListStart
                \resumeItem{Introduced VR, AR, and XR to public audiences trough workshops (GDJABARxITBxAgate) and interactive demonstrations (Toyota Goes to ITB, PRIMA ITB and ITB CEO Summit 2025). Developed STEI ITB's VR related projects. }
            \resumeItemListEnd
            
        \resumeSubheading
            {PT Bank Jago Tbk}{Jakarta, Indonesia}
            {IT Security Intern}{July 2024 \textbf{--} Sep 2024, Internship}
            \resumeItemListStart
                \resumeItem{Supported IAM operations across 40+ internal applications, covering User Access Reviews and PAM.}
                \resumeItem{Automated access review workflows with Google Apps Script, improving review efficiency by 80\% and strengthening compliance.}
            \resumeItemListEnd

        \resumeSubheading
            {Laboratorium Pemrograman STEI ITB}{Bandung, Indonesia}
            {Lab Assistant}{Feb 2023 \textbf{--} Jun 2025, Part-time}
            \resumeItemListStart        
                \resumeItem{Teaching Assistant \& Team Lead for core CS courses (Programming Fundamentals, Object-Oriented Programming, Algorithms \& Data Structures), mentoring 700+ students across practicums and final projects; provided hands-on guidance on core programming concepts to improve student comprehension and performance.}
                \resumeItem{Led a 5-person team, standardized evaluation workflows, and improved response time by 25\% through better coordination and process design.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd


%----------- EDUCATION -----------
\section{Education}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Institut Teknologi Bandung}{Bandung, Indonesia}
            {Master of Science in Informatics;                           \textbf{GPA: 3.65/4.00}}{2024 \textbf{--} Present}
        \vspace{.2pt}

        \resumeSubheading
            {Institut Teknologi Bandung}{Bandung, Indonesia}
            {Bachelor of Science in Information System and Technology;   \textbf{GPA: 3.68/4.00}}{2021 \textbf{--} 2025}
            \resumeSubHeadingListStart
            \small{\item{
                \textbf{Thesis:} Design and Implementation of a Grader Module in the Development of a Code Autograder System.}}
            \resumeSubHeadingListEnd
    
    \resumeSubHeadingListEnd


%----------- SKILLS -----------
\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Languages:}{ Python, TypeScript, SQL, HTML, Golang, C, C++, Java} \\ \vspace{1pt}
        \textbf{Technologies:}{ FastAPI, Flutter, React.js, Next.js, Vite, React Native, Expo, Tailwind CSS, Express, Hono, Prisma ORM, Drizzle, Docker, Kubernetes, RabbitMQ, Redis, MySQL, PostgreSQL, Firebase, Supabase, Google Cloud Platform, Playwright, Selenium, OpenAPI, Zod, OAuth} \\ \vspace{1pt}
    }}
  \resumeSubHeadingListEnd

\section{Languages}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Indonesia}{ (Native proficiency)} $\bullet$
        \textbf{English}{ (Full professional proficiency; TOEFL ITP: 620)} \\ \vspace{1pt}
    }}
  \resumeSubHeadingListEnd


%----------- PROJECTS -----------
\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Arkavidia 10} $|$ 
        \emph{\href{https://arkavidia.com/}{\color{blue}https://arkavidia.com}} $|$ 
        Technologies: Hono, Drizzle, Open API, Zod, oAuth, DigitalOcean, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Led a team of 32 people to create Arkavidia 9.0’s main website including front-end, back-end and infrastructure. In charge of solo infrastructure engineer and lead backend engineer (of 2 people).}
            \resumeItem{Accomodated 5000+ users registered with daily traffic reaching 500.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{HMIF App Backend} $|$ 
        \emph{\href{https://app.hmif.dev/}{\color{blue}https://app.hmif.dev}} $-$ \emph{\href{https://github.com/hmif-itb/hmif-app-be}{\color{blue}GitHub}} $|$ 
        Technologies: Hono, Drizzle, Open API, Zod, oAuth}{}
        \resumeItemListStart
            \resumeItem{REST API for Himpunan Mahasiswa Informatika’s internal PWA application. Served as the lead of backend developers with a team of 6 people.}
            \resumeItem{Used by 200+ active users monthly to access organizational information and activities.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Juragan Properti} $|$ 
        Technologies: Selenium, Flaresolverr, React, Next.js, Typescript}{}
        \resumeItemListStart
            \resumeItem{Website to predict Indonesian propert value based on geolocation, spatial, and facility characteristics. Done in part of a research study published at \href{https://www.emeraldgrouppublishing.com/journal/ijhma}{IJHMA}.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Ceruvia} $|$ 
        \emph{Inaccessable internal application} $-$ \emph{\href{https://github.com/Ceruvia/grader}{\color{blue}GitHub}} $|$ 
        Technologies: Go, Distributed Processing, GCP, Kubernetes}{}
        \resumeItemListStart
            \resumeItem{Webapp to accommodate STEI ITB’s need of automatic grading of student’s programming assessment as part of my bachelor thesis. In charge of the grader backend that operates as a code executor in a sandboxed environment and returns grade result; Also in changer of system deployment and scaling.}
            \resumeItem{Used by 500+ students weekly every semester.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{ITB Document Generator} $|$ 
        \emph{Inaccessable internal application} $|$ 
        Technologies: FastAPI, Jinja, Distributed Processing}{}
        \resumeItemListStart
            \resumeItem{Developed a distributed system with FastAPI and Celery for processing ITB's student academic documents.}
            \resumeItem{Integrated to ITB's main academic system (SIX ITB) and used yearly for 5000+ students.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{TwitterFetch} $|$ 
        \emph{\href{https://github.com/fawwazabrials/TwitterFetch}{\color{blue}https://github.com/fawwazabrials/TwitterFetch}} $|$ 
        Technologies: Python, Selenium, Playwright}{}
        \resumeItemListStart
            \resumeItem{Python module that scrapes tweets using a reverse engineered Twitter API with Playwright.} 
            \resumeItem{Used in media monitoring projects for \emph{BPK RI}, \emph{Pertamina}, \emph{Indonesian Ministry of Foreign Affairs}, and \emph{Indonesian Ministry of Transportation}.}
        \resumeItemListEnd
      
    \resumeSubHeadingListEnd

\section{Publications}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumePublicationHeading
            {Integrating Multi-Source Data and Explainable AI for Housing Market Analysis in Indonesia | \href{https://doi.org/10.1108/IJHMA-01-2026-0006}{\color{blue}10.1108/IJHMA-01-2026-0006}}
            {Mar 2026}
            {Ivan Aldy Ganesen, Muhamad Farhan Syakir, Fawwaz Abrial Saffa, Ayu Purwarianti and Nugraha Priya Utama}
            {International Journal of Housing Markets and Analysis (IJHMA), Emerald Publishing}
    \resumeSubHeadingListEnd

\end{document}
